Graphical formalization and automated computing of safety constraints in robotics

### 2012-08-11 paper/Paper.tex
add Bruce's initial
Updates from Bruce

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Ludwig N\"{a}gele}
\IEEEauthorblockA{Department of Software Engineering and\\Programming Languages\\ 
University of Augsburg\\
86135 Augsburg, Germany\\
Email: mail@ludwig-naegele.de}
\and
\IEEEauthorblockN{Bruce MacDonald}
\IEEEauthorblockA{Department of Electrical Engineering\\ 
The University of Auckland\\
Auckland 1142, New Zealand\\
Email: b.macdonald@auckland.ac.nz}
%\and
%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
%\IEEEauthorblockA{Starfleet Academy\\
%San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}
}

@@

%\IEEEPARstart{S}{afety}
Safety critical applications require extensive testing or formal verification in order to achieve adequate safe and predictable behavior.
Even if a more highlevel program has no physical movements and thus cannot directly cause any damage, its output might still be a trigger for dangerous actions executed by interacting actors.
%Even if a more highlevel program has no physical actors and thus cannot cause any damage, it might still have dangerous effects on the environment.
Imagine a medication reminder application which guides a person through the process of medication intake. All interaction is done by showing textual instructions on a display. An error in the program logic could cause an already taken medication to be reminded again and may injure an Alzheimer's diseased person by medication overdosage.
This example is taken from a healthcare robotics project at the University of Auckland, New Zealand. Scientists are working on applications such as the medication reminder~\cite{medicationreminder} which run on mobile robots serving in nursing homes for the elderly. Equipped with a touch display and several external devices such as a blood pressure measurement tool the robots aim to support and entertain the elderly in their daily activities~\cite{5649910}\cite{healtbot_new}.
The applications are meant to be developed by healthcare professionals using Robostudio~\cite{robostudio}, a visual programming environment for rapid authoring and customization of complex services on a personal service robot.
%state machine based processes and a graphical tool for the designing of human robot interaction.
Generally these people don't have profound knowledge of the complex mathematical syntax used for formal verification methods such as computation tree logic (CTL) or linear temporal logic (LTL). Nevertheless certain safety guarantees must somehow be delivered in order to gain users' trust and to prevent any harm or injuries by the healthbots.
In case of the medication reminder mentioned above it mitght be important to ensure notifications are sent to staff members whenever medication is not taken by the patient, or to avoid duplicate reminders for medications which have already been taken.

So we need a mechanism for the specification of such safety constraints which doesn't require special or expert knowledge and thus is easy to use for all kind of programmers. A visual language intended to fill this gap is presented in section~\ref{sec:visualformalism}.

@@

Also Del Bimbo et al. did work on a visual tool for temporal logic, but with a special focus on hierarchical representations of formulas~\cite{520786}. Here each node of a tree is described by an abstract operator whose subformulas are branches to their replacement operators. Thus the root node represents the entire formula. They also explored the formula trees' 3D representation within a virtual space.

Both approaches are different fundamental ideas of representing temporal formulas. Whereas having a graph and inputs and outputs seems not to be applicable for our approach, the idea of hirarchical operator representation of Del Bimbo et al. will be a good base for our try to find an easy to use concept for constraint creation and understanding.

@@

Even though this approach touches the subject of healthcare it barely matches our problem. HomeTL focuses rather on monitoring temporal boundaries of a patient's behavior than on ensuring functional safety of an implemented program. But it depicts how nontechnical constraint design can be realised and its graphical design gives a good example how to handle time dependencies.

@@

We want to introduce a visual language for the defining of safety constraints for state machine definition of robot behaviour which is suitable for non-experts in the formal methods domain. Ideally its appliance is easy to use and intuitive to read in order to facilitate maintainability.
Hence, the graphical formalism should abstract from the usually complex and mathematical concept of conventional formal methods but still stay unreduced in expressiveness compared to LTL as far as possible.

Furthermore a heuristic should be developed of how to identify reasonable constraints on an underlying state machine program. 
But since the particular domain distinguishes the significance of constraints respectively it might be difficult to show a universal heuristic working for all use cases. Hence, in this paper the concept of development support by constraint generation is examined within the domain of healthcare robotics. As a special requirement to the heuristic at least the following constraints are to be found for the medication reminder application:

\begin{itemize}
	\item The program will always eventually check the database for new reminder jobs. Thus we avoid that pending reminder are never processed.
	\item Either a reminded medication is taken properly or caregivers get notified whenever a patient refuses medication intake.
% The next item is left out so that we can say, our heuristic found one we didn't think about yet :)
%	\item During the medication intake process the program can not switch to other services such as entertainment mode ore blood pressure measurement, for example.
\end{itemize}

Some of the statements don't make sense of course if patients lie or pretend to take their medication. As our approach tries to validate state machine behaviour rather than human attitudes we assume correct collaboration or the use of tools which can recognize fairly medication intake. Furthermore also the correctness of external services used by the medication reminder such as the database module holding all reminders is not taken into account.

All the functionality mentioned above shall be combined in one editor and for evaluation purpose later be integrated into a programming environment for state machine editing.

@@

The presented visual language is made for expressing constraints for state machines. Similar to Del Bimbo's formula representation~\cite{520786}, a constraint consists of nested operators and propositions in a hierarchical manner. However we surrender the three dimensional idea and focus on two dimensional blocks and their compositions instead, what is also used by HomeTL~\cite{4341725}.
Each block represents either an operator or a proposition and has its specified semantics. Thus a visual formula can be recursively translated to a linear temporal logic (LTL) sentence and be checked using any ordinary model checker.

@@

Regarding to the requirements the visual language should be very easy to use, especially for non-experts. Furthermore it should provide an intuitive appliance which is ideally learnable within little time. So there are some design decisions an editor for this visual language has to fulfill:

\begin{itemize}
	\item Each operator has a different significant color flavor. This kind of classification enables a faster subconscious identification by the user.
	\item All editing is simply done by only drag and drop. Operators and propositions can be moved and dropped onto other operators. A tool bar provides all kinds of operator and proposition types to be instantiated and ideally a trash can for deleting existing operators.
	\item The layout of constraints (nested operators) has two dimensions with a certain meaning. Figure~\ref{fig:directions} demonstrates the ``logical'' vertical read direction as well as the time releveant horizontal line.
	\item In order to simplify the reading of constraints an operator can be hovered over by the mouse pointer. All higher operators become bleached out so that the hovered operator and its children appear highlighted. It's intended to be similar to line coloring when reading a digital text.
	\item Multiple nested operators of the same kind which have no order priorities such as \emph{OR} or \emph{AND} appeared to make the look unnecessarily complex. These operators can be merged as shown in figure~\ref{fig:nested_and}.
	\item Every edit to either the constraint or the underlying state machine results in an automatically (re-)validation of the constraint. The result is immediately displayed to the user.
	\item There is no button for constraint creation / editing except operator and proposition providers, which let the developer create new instances of them. Having no additional buttons reduces complexity and keeps it simple.
\end{itemize}

@@

In order to support the developer in specifying safety constraints, automated generation and suggestion of constraints might be helpful. But it's helpful only then, if the suggested constraints are relevant and reasonable. This however depends on the domain and use case.
Regarding to the postulated constraints in the requirements in section~\ref{sec:requirements} it turned out that all therefor relevant states have got one of the following characteristics:
%following types of states are of a special interest:

@@

In order to compute the required constraints and possibly even more of them automatically we manage with so called subgraphs defined as follows:
%Um die in requirements definierten constraints und vielleicht noch mehr zu finden, behelfen wir uns 
%Each $\alpha$-, the corresponding $\beta$- and several $\gamma$-states form a part of a state set called \emph{subgraph}. In order to retreive valid constraints a subgraph is defined by the following requirements: %as follows

\begin{itemize}
	\item It has a start state ($\alpha$-state) with at least two outgoing transitions.
	\item There is an end state ($\beta$-state) in which all possible paths starting from start state come together again.
	\item All states between start and end state have no other incoming transitions than the ones originally coming from start state. That means there is no path to visit these states exept through start state.
	\item start state may have incoming transitions from states not contained in the subgraph.
	\item end state may have incoming and outgoing transitions from and to states not contained in the subgraph.
\end{itemize}

@@

Using this specification all possible subgraphs can be detected within a state machine. If a subgraph contains neither inner (infinite) loops nor final states (states having no outgoing transition) we can derive the following valid LTL formulas for each subgraph (with $\alpha$ as proposition for ``$\alpha$ is current state'' and similarily for $\beta$ and all $\gamma$'s):

@@

All formulas can be translated to the visual formalism presented in section~\ref{sec:visualformalism} and shown to the user. The accordant LTL formulas for the postulated constraints in section~\ref{sec:requirements} belong to number \ref{eq:second} and \ref{eq:fifth} of the subgraph based formula templates and are as follows:

@@

To experience and evaluate the visual formalism as well as the usefulness of constraint generation we developed an editor which provides functionalities all proposed functionalities while taking the requirements into account.
It's implemented as a java swing component, making it easy to integrate the visual language into other java applications. An API allows to set the underlying state machine what also influences the state propositions available for constraint editing. Furthermore a particular model checker can be specified to be used for constraint validation. As default, the symbolic model checker NuSMV~\cite{springerlink:10.1007/s100090050046}~\cite{NuSMV2} is used for constraint validation.

Figure~\ref{fig:editor} shows a snapshot of the editor's environment: All functionality needed for constraint editing is provided in the tool bar on the right which contains drag providers for the creating of all operator and proposition types as well as a trash for deleting. Constraints can be composed in the dashboard in the middle of the editor by drag and drop. The tab functionality on the left allows to manage several constraints. Each tab schows a small thumbnail of the constraint and a symbol indicating its validity what is a warning shield for ``incomplete'', a green shield for ``valid'', a red cross for ``invalid'' or an animated ring for ``validation in progress''. The magic wand button within the tab pane triggers the constraint generation.

@@

In order to evaluate the proposed safety functionalities on various programs the tool was integrated into Robostudio~\cite{robostudio}. It allows the specification of state machine based programs whose behaviour can then be examined by visual constraints. As an example of how to use them we will have a closer look at the simplified medication reminder application whose underlying screen-flow is explained in figure~\ref{fig:medicationreminder}. Starting from ``Menu'' the user can choose from several services such as blood pressure measurement ore entertainment mode. In the given example these services are simplified to just one state ``additional services'' since we want to focus only on the medication reminder part. In ``Polling'' the database is checked for a pending reminder, and if there is one the medication intake guidance is triggered. The patient can state if he's already taken his medication, or decide whether he wants to take it or not. In the latter he may give a reason for it and a caregiver gets notified about this incident. Otherwise it will result in ``Well done!'' after completing intake.

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\linewidth]{stm} %width=0.7\linewidth
  \caption{Simplified screen-flow of the medication reminder application.}
  \label{fig:medicationreminder}
\end{figure}

@@

Owing to the elaborated performance of NuSMV even the validation of constraints on huge and complex programs is fast and allows quick feedback. Besides, the validation itself runs in background without locking the dashboard. Therefore we got rid of waiting times and disruptions during constraint development what would be very well the case with conventional model checking where constraint development and constraint validation are alternating occupations. Thus it's considered as an improvement of user experience.

@@

The automated constraint generation can be triggered by a click on the magic wand button in the tab area. After activation a dashboard gets opened in a new tab for each found constraint, and validation is initiated immediately. In case of the medication reminder application six constraints are found, whereof \emph{A)} and \emph{B)} shown in figure~\ref{fig:generatedconstraints} are actually matching the postulations in the requirements in section~\ref{sec:requirements}.
The constraint used for demonstration in the previous chapter gets also generated, however \emph{B)} forms an intensified restriction of it.

Constraint \emph{A)} ensures the ``Polling'' state to be always eventually visited again. If a pending medication is not already taken, constraint \emph{B)} guarantees intake or staff notification before next reminders can be read from database.

We showed that the subgraph approach is working for the medication reminder application, and there was even one more reasonable constraint found by the heuristic: Constraint \emph{C)} ensures that during the medication intake process the program can not switch back to the menu or other services such as entertainment mode ore blood pressure measurement.

@@

The editor presented in this paper proofes validity of all constraints and presents the result \emph{valid} or \emph{invalid} to the user. But in contrast to conventional model checking no additional explanation for the outcome such as a counter example is given. It can be considered to extend the visual language with support for bug identification by a visualization of counter examples, for example.
%\item Substitution of parts of constraints would be nice in order to make it easier to understand. (A simple operator which abstracts from a more complex operator). It's comparable to composite states of hirachical state machines.

@@

@@

In this paper we represented a visual formalism for the defining of safety constraints and a concept of automated constraint generation. Both features are implemented and assembled in an editor for standalone or integration use. The visual language is pretty simple what makes it accessible to a wider range of software developers. Nevertheless its expressiveness is fairly powerful and allows serious model checking.

The concept of constraint generation worked very well for our use case the medication reminder application and all postulated constraints were found. Since we even discovered a new reasonable constraint we are convinced this concept as well as the visual language for constraint defining can be a beneficial supporting thing for plenty of developers.

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Ludwig N\"{a}gele}
\IEEEauthorblockA{Department of Software Engineering and\\Programming Languages\\ 
University of Augsburg\\
86135 Augsburg, Germany\\
Email: mail@ludwig-naegele.de}
\and
\IEEEauthorblockN{Bruce A. MacDonald}
\IEEEauthorblockA{Department of Electrical Engineering\\ 
The University of Auckland\\
Auckland 1142, New Zealand\\
Email: b.macdonald@auckland.ac.nz}
%\and
%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
%\IEEEauthorblockA{Starfleet Academy\\
%San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}
}

@@

%\IEEEPARstart{S}{afety}
Safety critical applications require extensive testing or formal verification in order to achieve adequate safe and predictable behavior.
Even if a more highlevel program has no physical movements and thus cannot directly cause any damage, its output might still be a trigger for dangerous actions executed by interacting actors.
%Even if a more highlevel program has no physical actors and thus cannot cause any damage, it might still have dangerous effects on the environment.
Imagine a medication reminder application which guides a person through the process of medication intake, such as the healthcare robotics project at the University of Auckland, New Zealand \cite{jayawardena12:_desig}. All interaction is by showing textual instructions on a display, and by speech generation. An error in the program logic could cause an already taken medication to be reminded again and may injure a patient with Alzheimer's disease by causing a medication overdose.
Scientists are working on applications such as the medication reminder~\cite{p11:_feasib} which run on mobile robots serving in nursing homes for the elderly. Equipped with a touch display and several external devices such as a blood pressure measurement tool the robots aim to support and entertain the elderly in their daily activities~\cite{jayawardena12:_desig,5649910}.
The applications are intended to be developed by healthcare professionals using Robostudio~\cite{robostudio}, a visual programming environment for rapid authoring and customization of complex services on a personal service robot.
%state machine based processes and a graphical tool for the designing of human robot interaction.
Generally these people don't have profound knowledge of the complex mathematical syntax used for formal verification methods such as computation tree logic (CTL) or linear temporal logic (LTL). Nevertheless certain safety guarantees must somehow be delivered in order to gain users' trust and to prevent any harm or injuries by the healthcare robots.
In case of the medication reminder mentioned above it might be important to ensure notifications are sent to staff members whenever medication is not taken by the patient, or to avoid duplicate reminders for medications which have already been taken.

So a mechanism is needed for the specification of such safety constraints; one that does not require special or expert knowledge and thus is easy to use for all kind of programmers. A visual language intended to fill this gap is presented in section~\ref{sec:visualformalism}.

@@

Also Del Bimbo {\em et al} worked on a visual tool for temporal logic, but with a special focus on hierarchical representations of formulas~\cite{520786}. Here each node of a tree is described by an abstract operator whose subformulas are branches to their replacement operators. Thus the root node represents the entire formula. They also explored the formula trees' 3D representation within a virtual space.

Both approaches are different fundamental ideas of representing temporal formulas. Whereas having a graph and inputs and outputs seems not to be applicable for our approach, the idea of hirarchical operator representation of Del Bimbo {\em et al} will be a good basis for our concept of constraint creation and understanding.

@@

Even though this approach touches the subject of healthcare it barely matches our problem. HomeTL focuses more on monitoring temporal boundaries of a patient's behavior than on ensuring functional safety of an implemented program. It does depict how nontechnical constraint design can be realised and its graphical design is a good example of handling time dependencies.

@@

We want to introduce a visual language for defining safety constraints in state machine definitions of robot behaviour, that is suitable for people who are not experts in formal methods. The visual language should be easy to use and intuitive to read, in order to facilitate maintainability.
Hence, the graphical formalism should abstract from the usually complex and mathematical concept of conventional formal methods but still be unreduced in expressiveness compared to LTL, so far as possible.

Furthermore a heuristic should be developed, which identifies reasonable constraints on an underlying state machine program. 
Since the particular domain semantics distinguish the significance of constraints, it may be difficult to show a universal heuristic. Hence, in this paper the concept of development support by constraint generation is examined within the domain of healthcare robotics. As a special requirement for the heuristic at least the following constraints are to be found for the medication reminder application:

\begin{itemize}
	\item The program will always eventually check the database for new reminder jobs. Thus we ensure that pending reminders are processed.
	\item Either a reminded medication is taken properly, or caregivers are notified that the patient refused medication intake.
% The next item is left out so that we can say, our heuristic found one we didn't think about yet :)
%	\item During the medication intake process the program can not switch to other services such as entertainment mode ore blood pressure measurement, for example.
\end{itemize}

Some of the statements do not make sense if patients lie or pretend to take their medication but don't take it. As our approach validates state machine behaviour rather than human attitudes we assume there is either cooperation from the patient or a separate tool that can verify medication intake. Furthermore we assume the correctness of external services used by the medication reminder such as the database module holding all reminders.

% Bruce: I'm not sure we need this sentence. I think you have integrated it now anyway.
% All the functionality mentioned above shall be combined in one editor and for evaluation purpose later be integrated into a programming environment for state machine editing.

@@

** COMMENT: This is a comment between the double stars; can delete it when you read it. I think we need a statement about the design here; I have tried to draft it; you may likely be able to improve! It should link the requirements to the design; I think that is pretty straightforward so just need a simple statement I think. ** 
The presented visual language is designed to express constraints for state machines. To provide the required functionality, the fundamental logical operators are required, as shown in (a) though (e) below. In addition the visual language should be capable of expressing constraints about future steps, both (f) any future state and (h) the next state, that (g) events should always happen, and that (h) a property must be true until some future event.

 Like Del Bimbo {\em et al's} formula representation~\cite{520786}, a constraint consists of nested operators and propositions in a hierarchy. However we surrender the three dimensional idea and focus on two dimensional blocks and their compositions instead, what is also used by HomeTL~\cite{4341725}.
Each block represents either an operator or a proposition and has its specified semantics. Thus a visual formula can be recursively translated to a linear temporal logic (LTL) sentence and be checked using any ordinary model checker.

@@

To meet the requirements the visual language should be very easy to use, especially for non-experts. Furthermore it should provide an intuitive application which is ideally learnable within little time. So there are some design decisions an editor for this visual language must fulfill:

\begin{itemize}
	\item Each operator has a different significant visual appearance; in this case we have used color. This kind of classification enables a faster subconscious identification by the user. ** COMMENT: can you refer to a GUI design text book regarding this? And how about colour blindness? Don't get me wrong; I am very happy with it; just could do with some citation about it. **
	\item All editing is performed only by simple drag and drop. Operators and propositions can be moved and dropped onto other operators. A tool bar provides all operator and proposition types to be instantiated and there is a trash can for deleting existing operators.
	\item The layout of constraints (nested operators) has two dimensions with a certain meaning. Figure~\ref{fig:directions} demonstrates the ``logical'' vertical read direction as well as the time releveant horizontal line.
	\item In order to simplify the reading of constraints an operator can be hovered over by the mouse pointer. All higher operators become bleached out so that the hovered operator and its children appear highlighted. It's intended to be similar to line coloring when reading a digital text.
	\item Multiple nested operators of the same kind which have no order priorities such as \emph{OR} or \emph{AND} appear unnecessarily complex. These operators can be merged as shown in figure~\ref{fig:nested_and}.
	\item Every edit to either the constraint or the underlying state machine results in an automatically (re-)validation of the constraint. The result is immediately displayed to the user.
	\item There is no button for constraint creation / editing except operator and proposition providers, which let the developer create new instances. Having no additional buttons reduces complexity and keeps it simple.
\end{itemize}

@@

In order to support the developer in specifying safety constraints, automated generation and suggestion of constraints might be helpful. But it's helpful only if the suggested constraints are relevant and reasonable. This however depends on the domain and use case.
Regarding the postulated constraints in the requirements in section~\ref{sec:requirements} all the relevant states have one of the following characteristics:
%following types of states are of a special interest:

@@

In order to compute the required constraints automatically, and possibly additional ones, we manage a set of subgraphs defined as follows:
%Um die in requirements definierten constraints und vielleicht noch mehr zu finden, behelfen wir uns 
%Each $\alpha$-, the corresponding $\beta$- and several $\gamma$-states form a part of a state set called \emph{subgraph}. In order to retreive valid constraints a subgraph is defined by the following requirements: %as follows

\begin{itemize}
	\item It has a start state ($\alpha$-state) with at least two outgoing transitions.
	\item There is one ** COMMENT: one not an? ie can only be one? ** end state ($\beta$-state) in which all possible paths starting from start state come together again.
	\item All states between the start and end states have no other incoming transitions than the ones originally coming from the start state. That means there is no path to visit these states except through the start state.
	\item The start state may have incoming transitions from states not contained in the subgraph.
	\item The end state may have incoming and outgoing transitions from and to states not contained in the subgraph.
\end{itemize}

@@

Using this specification all possible such subgraphs can be detected within a state machine. If the subgraph contains neither inner (infinite) loops nor final states (states having no outgoing transition) we can derive the following valid LTL formulas for each subgraph (with $\alpha$ as proposition for ``$\alpha$ is current state'' and similarily for $\beta$ and all $\gamma$'s):

@@

All formulas can be translated to the visual formalism presented in section~\ref{sec:visualformalism} and shown to the user. The appropriate LTL formulas for the postulated constraints in section~\ref{sec:requirements} belong to number \ref{eq:second} and \ref{eq:fifth} of the subgraph based formula templates and are as follows:

@@

To explore and evaluate the visual formalism as well as the usefulness of constraint generation we developed an editor which provides all proposed functionality while taking the requirements into account.
The implementation is a java swing component, making it easy to integrate the visual language into other java applications. An API enables an underlying state machine which also influences the state propositions available for constraint editing. Furthermore a particular model checker can be specified for constraint validation. As a default, the symbolic model checker NuSMV~\cite{springerlink:10.1007/s100090050046,NuSMV2} is used.

Figure~\ref{fig:editor} shows a snapshot of the editor's environment: All functionality needed for constraint editing is provided in the tool bar on the right which contains drag providers for the creating of all operator and proposition types as well as a trashcan for deleting. Constraints can be composed in the dashboard in the middle of the editor by drag and drop. The tab functionality on the left allows several constraints to be managed. Each tab shows a small thumbnail of the constraint and a symbol indicating its validity, which is a warning shield for ``incomplete'', a green shield for ``valid'', a red cross for ``invalid'' or an animated ring for ``validation in progress.'' The magic wand button within the tab pane triggers the constraint generation.

@@

In order to evaluate the proposed safety functionality the tool was integrated into Robostudio~\cite{robostudio}. It allows the specification of state machine based programs whose behaviour can then be examined by visual constraints. As an example we consider the simplified medication reminder application whose underlying screen-flow is explained in figure~\ref{fig:medicationreminder}. Starting from ``Menu'' the user can choose from several services such as blood pressure measurement or entertainment. In the given example these services are simplified to just one state ``additional services'' since we want to focus only on the medication reminder part. In ``Polling'' the database is checked for a pending reminder, and if there is one the medication intake guidance is triggered. The patient can state if he or she has already taken the medication, or decide whether to take it or not. In the latter he or she may give a reason for it and a caregiver is notified about this incident. Otherwise it will result in ``Well done!'' after completing intake.

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\linewidth]{stm} %width=0.7\linewidth
  \caption{Simplified screen-flow of the medication reminder application. ** COMMENT: THIS ONE IS TOO SMALL! SHOULD MAKE IT BIGGER TO MAKE TEXT READABLE **}
  \label{fig:medicationreminder}
\end{figure}

@@

NuSMV performs well so even the validation of constraints on huge and complex programs is fast and allows rapid feedback. In addition, the validation itself runs in the background without locking the dashboard. Therefore we have removed waiting times and disruptions during constraint development, which would be likely with conventional model checking where constraint development and constraint validation are alternating processes. Thus we consider our tools an improvement for the users' experience.

@@

The automated constraint generation can be triggered by a click on the magic wand button in the tab area. After activation a dashboard is opened in a new tab for each found constraint, and validation is initiated immediately. For the medication reminder application six constraints are found, including \emph{a)} and \emph{b)} shown in figure~\ref{fig:generatedconstraints} which match the postulations in the requirements in section~\ref{sec:requirements}.
The constraint used for demonstration in the previous section is also generated, however \emph{b)} forms an intensified restriction of it.

Constraint \emph{a)} ensures the ``Polling'' state is always eventually visited again. If a pending medication is not already taken, constraint \emph{b)} guarantees intake or staff notification before the next reminders can be read from the database.

We showed that the subgraph approach is working for the medication reminder application, and there was even one more reasonable constraint found by the heuristic: Constraint \emph{c)} ensures that during the medication intake process the program can not switch back to the menu or other services such as entertainment or blood pressure measurement.

** COMMENT: Possible comment here about the scalability and practicality about constraint generation; do you think it will explode in larger cases? Either way a comment might be useful. **

@@

The editor presented in this paper proves validity of all constraints and presents the result \emph{valid} or \emph{invalid} to the user. But in contrast to conventional model checking no additional explanation for the outcome such as a counter example is given. It can be considered to extend the visual language with support for bug identification by a visualization of counter examples, for example.
%\item Substitution of parts of constraints would be nice in order to make it easier to understand. (A simple operator which abstracts from a more complex operator). It's comparable to composite states of hirachical state machines.

@@

A more systematic evaluation of the tool is required, however this is beyond the scope of the current project. Now that a visual language and tool have been proposed, the next step is to evaluate the tool on a number of applications, make any required modications, then evaluate the tool in a user study for healthcare robotic applications.

@@

In this paper we represented a visual formalism for the defining of safety constraints and a concept of automated constraint generation. Both features are implemented and assembled in an editor for standalone or integrated use. The visual language is reasonably simple which makes it accessible to a wider range of software developers. Nevertheless it is reasonably expressive and allows serious model checking.

The concept of constraint generation worked very well for our use case, the medication reminder application, and all postulated constraints were found. Since we even discovered a new reasonable constraint we are convinced this concept as well as the visual language for defining constraints has the potential to support development of safety critical healthcare robot applications.
